Magnetic propeties of a two dimentional electron gas strongly coupled to lights

### 2021-05-20 theory/sec_06.tex
Finalize conductivity equation
Add yy conductivity

Howver, we are only consider the transverse conductivity in $x$ direction we can identify that $x$ directional current operator as

@@

\noindent
For electric current operator we can introduce the electron's charge and effective mass
\begin{equation} \label{6.15}
  \begin{aligned}
    \qty({j}^x_{s=0})_{nm,n'm'} & =
    \frac{e^2B}{{m}}
    \delta_{k_x,k'_x}
    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1})
  \end{aligned}
\end{equation}
\hfill$\blacksquare$

>>>>

Let's consider the transverse conductivity in $x$ direction and we can identify that $x$ directional current operator as

@@

\noindent
For electric current operator we can introduce the electron's charge and effective mass
\begin{equation} \label{6.16}
  \begin{aligned}
    \qty({j}^x_{s=0})_{nm,n'm'} & =
    \frac{e^2B}{{m_e}}
    \delta_{k_x,k'_x}
    \qty(\sqrt{\frac{n+1}{2}} \delta_{n',n+1} + \sqrt{\frac{n}{2}}
    \delta_{n',n-1})
  \end{aligned}
\end{equation}
\hfill$\blacksquare$

\noindent
Next we can consider the transverse conductivity in $y$ direction and we can identify that $y$ directional current operator as
\begin{equation} \label{6.17}
  \hat{j}_y = \frac{1}{m} \qty(-i\hbar\pdv{y} - \frac{eE}{\omega}\cos(\omega t)).
\end{equation}
Now we can calculate the matrix elements of $y$ directional current operator's matrix in Floquet mode basis as
\begin{equation} \label{6.18}
  \qty({j}_y)_{nm,n'm'} = \mel{n,k_x}{\;\hat{j}_y\;}{n',k'_x} =
  \mel{n,k_x}{\;\frac{-1}{m} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))\;}{n',k'_x}
\end{equation}
and we can evaluate these using Floquet modes derived in Eq.\eqref{3.15} as follows
\begin{equation} \label{6.19}
  \begin{aligned}
    \qty({j}_y)_{nm,n'm'} & =
    \int dx \int dy \;
    \frac{1}{\sqrt{L_x}} \chi_{n}\big(y - y_0 - \zeta(t)\big)
    \exp(-ik_x x) \\
    & \times
    \frac{-1}{m} \qty(i\hbar\pdv{y} + \frac{eE}{\omega}\cos(\omega t))
    \frac{1}{\sqrt{L_x}} \chi_{n'}\big(y - y_0 - \zeta(t)\big)
    \exp(i k'_x x)
  \end{aligned}
\end{equation}
then introducing new variable
\begin{equation} \label{6.20}
  y - y_0 - \zeta(t) = \bar{y} \quad \longrightarrow \quad dy = d{\bar{y}}
\end{equation}
and follwing identity [*Ref: Appendix A Hermite fucntions]
\begin{equation} \label{6.21}
  \pdv{\chi_n(y)}{y} = -\sqrt{\frac{n+1}{2}} \chi_{n+1}(y) +
  \sqrt{\frac{n}{2}} \chi_{n-1}(y)
\end{equation}
above expression can be simplified as previous case (let $y=\bar{y}$)
\begin{equation} \label{6.22}
  \begin{aligned}
    \qty({j}_y)_{nm,n'm'} & =
    \frac{-1}{{m}}
    \delta_{k_x,k'_x}
    \int dy \;
     \chi_{n}(y)
    \qty[-i\hbar \qty(
    \sqrt{\frac{n'+1}{2}} \chi_{n'+1}(y) - \sqrt{\frac{n'}{2}} \chi_{n'-1}(y)
    ) + \frac{eE}{\omega}\cos(\omega t)
    \chi_{n'}(y)].
  \end{aligned}
\end{equation}
Then considering Gauss-Hermite integral indentities we can derive that
\begin{equation} \label{6.23}
  \begin{aligned}
    \qty({j}_y)_{nm,n'm'} & =
    \frac{1}{{m}}
    \delta_{k_x,k'_x}
    \qty[i\hbar \qty(
    \sqrt{\frac{n'+1}{2}} \delta_{n,n'+1}
    - \sqrt{\frac{n'}{2}} \delta_{n,n'-1}
    ) - \frac{eE}{\omega}\cos(\omega t) \delta_{n,n'}]
  \end{aligned}
\end{equation}
\textcolor{red}{Due to complexity we can only consider the constant contribution and we allows only the one-cycle averaged current flow} and then we can derive the $s=0$ components of the Fourier series as
\begin{equation} \label{6.24}
  \begin{aligned}
    \qty({j}^y_{s=0})_{nm,n'm'} & =
    \frac{1}{T} \int_0^T dt \;
    \frac{1}{{m}}
    \delta_{k_x,k'_x}
    \qty[i\hbar \qty(
    \sqrt{\frac{n'+1}{2}} \delta_{n,n'+1}
    - \sqrt{\frac{n'}{2}} \delta_{n,n'-1}
    ) - \frac{eE}{\omega}\cos(\omega t) \delta_{n,n'}]
  \end{aligned}
\end{equation}
and this can be evaluate and get
\begin{equation} \label{6.25}
  \begin{aligned}
    \qty({j}^y_{s=0})_{nm,n'm'} & =
    \frac{i\hbar}{{m}}
    \delta_{k_x,k'_x}
    \qty[
    \sqrt{\frac{n'+1}{2}} \delta_{n,n'+1}
    - \sqrt{\frac{n'}{2}} \delta_{n,n'-1}
    ]
  \end{aligned}
\end{equation}
and this can be re-write as
\begin{equation} \label{6.26}
  \begin{aligned}
    \qty({j}^y_{s=0})_{nm,n'm'} & =
    \frac{i\hbar}{{m}}
    \delta_{k_x,k'_x}
    \qty[
    \sqrt{\frac{n}{2}} \delta_{n',n-1}
    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
    ]
  \end{aligned}
\end{equation}

\noindent
For electric current operator we can introduce the electron's charge and effective mass
\begin{equation} \label{6.27}
  \begin{aligned}
    \qty({j}^y_{s=0})_{nm,n'm'} & =
    \frac{ie\hbar}{{m}}
    \delta_{k_x,k'_x}
    \qty[
    \sqrt{\frac{n}{2}} \delta_{n',n-1}
    - \sqrt{\frac{n+1}{2}} \delta_{n',n+1}
    ]
  \end{aligned}
\end{equation}
\hfill$\blacksquare$

xx
